Order Reduction and MILP Models for Real-Time DNN Robustness Certification \\ Supplementary Material

### 2025-08-05 AAAI2026/Sup.tex
capitalize section headings

\title{Order reduction and MILP models for real-time DNN robustness certification. \\ Supplementary Material}
\date{}
\author{
	%Authors
	% All authors must be in the same font size and format.
	Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{With help from the AAAI Publications Committee.}\\
	AAAI Style Contributions by Pater Patel Schneider,
	Sunil Issar,\\
	J. Scott Penberthy,
	George Ferguson,
	Hans Guesgen,
	Francisco Cruz\equalcontrib,
	Marc Pujol-Gonzalez\equalcontrib
}
\affiliations{
	%Afiliations
	\textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\
	% If you have multiple authors and multiple affiliations
	% use superscripts in text and roman font to identify them.
	% For example,

@@

	\iffalse
	\begin{abstract}
		\input{abstract.tex}

		Most DNNs are brittle to small perturbations. Extensive works have thus been performed to verify robustness for DNNs.
		However, these works mostly consider local robustness, i.e. in the neighborhood of an image.
		While local robustness is useful to have an idea how often non robust images happen, by repeating the verification on 1000 or 10000 pre-obtained images, the main shortcoming is that we have no guarantee that a specific new incoming image, e.g. in a video feed, is robust: The verification process takes too long and requires too much resources to be performed online on embedded systems.

		In this paper, we consider {\em global} robustness, that is, guarantees not restricted to a set of local images. For that, we consider {\em bounds} on the switch of values between the different decision classes of a DNN due to a given perturbation. 
		The verification question is much harder than local robustness, as the number of complex variables doubles (from the deviation image to the image and its deviation).
		Further, the values each neuron can take is no more in a small neighborhood.
		Therefore, the global verification process is very complex.
		To obtain useable bounds, we develop several novel partial MILP models for global robustness, with different trade-offs. Last, we use order reduction techniques to reduce the space of images considered, avoiding unrealistic inputs, by using linear PCA. 
		This results into usable bounds, allowing in real time to certify robustness for $87\%$ of incoming images in the MNIST benchmark for a L1-perturbation of $0.5$, as well as for a surrogate computing the hidden plastic strain associated to a deformation map of a pipe.
	\end{abstract}
	\fi

@@

Case 1: if $a = 1$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 4.

Case 2: if $a = 1$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i+x'_i$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 6.

Case 3: if $a = 0$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = 0$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 3.

Case 4: if $a = 0$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = -x'_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 5.

>>>>

\title{Order Reduction and MILP Models for Real-Time DNN Robustness Certification \\ Supplementary Material}
\date{}
\author{
	%Authors
	% All authors must be in the same font size and format.
	Written by AAAI Press Staff\textsuperscript{\rm 1}\thanks{With help from the AAAI Publications Committee.}\\
	AAAI Style Contributions by Pater Patel Schneider,
	Sunil Issar,\\
	J. Scott Penberthy,
	George Ferguson,
	Hans Guesgen,
	Francisco Cruz\equalcontrib,
	Marc Pujol-Gonzalez\equalcontrib
}
\affiliations{
	%Afiliations
	\textsuperscript{\rm 1}Association for the Advancement of Artificial Intelligence\\
	% If you have multiple authors and multiple affiliations
	% use superscripts in text and roman font to identify them.
	% For example,

@@

@@

\textbf{Case 1:} if $a = 1$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 4.

\textbf{Case 2:}  if $a = 1$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\geq 0$, then we need to show $\hat{y}_i = y_i+x'_i$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 6.

\textbf{Case 3:} if $a = 0$ and $a' = 0$, then $x'_i \leq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = 0$ based on  $\hat{x'_i} = 0$. This is true by the two inequalities in line 3.

\textbf{Case 4:} if $a = 0$ and $a' = 1$, then $x'_i \geq 0 $ and $y_i+x'_i\leq 0$, then we need to show $\hat{y}_i = -x'_i$ based on  $\hat{x'_i} = x'_i$. This is true by the two inequalities in line 5.
